Adopting agile software development in the large organizations: A systematic literature review

### 2014-08-13 journal/content.tex
Discussion

In this chapter we discuss the results and provide a conclusion on this work.
First the results are discussed, including highlighting of most important
findings and comparison to previous work. Then we present limitations and
threats to the validity of this work. This chapter ends with a concluding
overview of the work.

@@

Grounded theory may not be able to provide a generally applicable models for
agile transformation, at least not in a literature review made based on the
current agile transformation publications. This is because of two things.
First, the organizations seem to differ too much from each other. Secondly, the
published studies focus too much on isolated phenomena within the larger
transformation.
It would require too big of an interpretation to combine all the various cases
into one theoretical model. For these reasons we chose to present
transformations using an elementary two-axial classification of transformations,
and listings of individual phenomena that typically occur in a transformation.

@@

Even if the primary studies do not include rigorous research methods, their
authors have chosen to bring up matters that they consider important. It can be
argued that if a matter is being talked about it must be of some significance.
We believe that the viewpoints on agile transformation that have been elicitated
in this research are the ones to discuss.
In order to strengthen the evidence, we included only viewpoints that are
discussed in several studies.
There may be other factors affecting transformation, but this study provides
evidence that these are the most important ones.

Transformation and scaling up are related concepts. Although this research
focuses on transformation process only, it can not be completely separated from
discussion on scaling up, or on large-scale agile implementation in general.
Examples on where scaling up can be seen as the transformation itself are
organizations which start with a successful pilot project, after which agile
methods are introduced step wise to the rest of the organization.

% ------------------------------

% Comparison with literature

\citet{Misra2010} states that an agile adoption requires a change in mindset.
--> What evidence on this was there?

The higher level of coordination required in a large organization compared to
ideal small agile organizations was showing.

* Vertailu kirjallisuuteen

* What is similar in organizations of all scales?

* What is special in large scale?

* Customization of practices was seen as necessary, as large scale has demands
  over the original agile ideas

* It can be argued that any development effort with hundreds of teams will be
  difficult to coordinate

% Related challenges and success factors

It is evident in the results that some success factors and challenges relate.
Some success factors and challenges are complementary, so that lack of some
factor is a challenge, but availability of it provides success.
A particular complementary relationship could be observed in use of training

* Success factors and challenges may be complements, and may be presented as
  complements

* Have flexibility for different teams in the agile model (agile found
  hard [P41]) vs. conformity to a single model.

% ?

* Transformation of an organization to use agile can be seen as transforming
  also the agile method to suit the organization.
  --> A large-scale agile model may require tailoring and trial over time

>>>>

In this chapter we discuss the results and provide a conclusion on this work.
First the results are discussed, including highlighting some findings and
comparison to previous work. Then we present an appraisal of limitations and
threats to the validity of this work. This chapter ends with a concluding
overview of the work.

@@

The discussion of the results is divided into several sections, each bringing up
a particular viewpoint. The first part of this section focuses on interpretation
of results and comparison to the background literature. The remainder of this
section discusses problems that were encountered during the research process.

\subsection{Related challenges and success factors}

It is evident in the results that some success factors and challenges relate.
Some success factors and challenges are complementary, so that lack of some
factor is a challenge, but availability of it provides success.
A particular complementary relationship was apparent in use of training
and coaching. The lack of training was seen as a challenge, and similarly
investments in training were reported as a success factor.

Another complementary relationship could be observed in discussion on
requirements management. Implementing effective requirements breakdown and
long term requirements planning were seen as challenges. The complementary
success factor was to pay close attention on how the Product Owner role 
was implemented.

Yet another complementary relationship was observed in that implementing the
agile model was found to be difficult, but choosing the the agile methods
carefully was seen as a success factor. Implementation difficulties were due to
misconceptions on agile and lack of guidance on how to proceed during the agile
transformation. Complementing these challenges primary studies emphasized
using care in choosing the agile model to pursue.

% * Have flexibility for different teams in the agile model (agile found
%   hard [P41]) vs. conformity to a single model.

The significance of the complementary challenges and success factors can be
interpreted in a few ways. The simplest interpretation is that success factors
in transformation that have complementing challenges have a higher significance.
This means that investment in training and coaching should be considered as a
significant success factor. Similarly, paying attention to requirements
management and especially the Product Owner role can be considered as
significant success factors. The relationship between implementation challenges
with the agile model and the success factors related to careful choice of the
model may not indicate greater significance. Instead the connection between
these challenges and success factors can be considered to indicate that they
simply should be studied together.

\subsection{Comparing results with existing literature}

Implementing an agile model is more about a change in mindset than application
of a set of new practices \citep{Misra2010}. Although this is an important point
in discussion on agile transformations, it was discussed quite little in the
primary studies. However, the use of coaching was a particular practice that was
aimed towards changing the mindset of people. A particular viewpoint that was
brought up when presenting coaching as a success factor was the importance of
how coaching could create a change in mindset. Coaching was attributed as a way
to teach by practice how to apply an agile mindset in development.

A particular complication in this research was distinguishing between the
concepts of transformation and scaling up. Distinguishing between these concepts
was an important factor due to the systematic nature of this research. Although
this research focuses on transformation process only, it can not be completely
separated from discussion on scaling up, or on large-scale agile implementation
in general.
Examples on where scaling up can be seen as the transformation itself are
organizations which start with a successful pilot project, after which agile
methods are introduced step wise to the rest of the organization.

@@

Even if the primary studies do not include rigorous research methods, their
authors have chosen to bring up matters that they consider important. It can be
argued that if a matter is being talked about it must be of some significance.
We believe that the viewpoints on agile transformation that have been elicited
in this research are the ones to discuss.
In order to strengthen the evidence, we included only viewpoints that are
discussed in several studies.
There may be other factors affecting transformation, but this study provides
evidence that these are the most important ones.

\subsection{Problems using grounded theory for analyzing distinctive organizations}

Grounded theory may not be able to provide a generally applicable models for
agile transformation, at least not in a literature review made based on the
current agile transformation publications. This is because of two things.
First, the organizations seem to differ too much from each other. Secondly, the
published studies focus too much on isolated phenomena within the larger
transformation.
In our case it would require too big of an interpretation to combine all the
various cases into a theoretical model. For these reasons we chose to present
transformations using an elementary two-axial classification of transformations,
listings of individual phenomena, and other typical factors in transforming
organizations.

% * What is similar in organizations of all scales?
% 
% * What is special in large scale?
% 
% The higher level of coordination required in a large organization compared to
% ideal small agile organizations was showing.
% 
% * It can be argued that any development effort with hundreds of teams will be
%   difficult to coordinate
% 
% * Customization of practices was seen as necessary, as large scale has demands
%   over the original agile ideas

% ???
% 
% * Transformation of an organization to use agile can be seen as transforming
%   also the agile method to suit the organization.
%   --> A large-scale agile model may require tailoring and trial over time
